Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-03 FDT2020/Introduction.tex
Adding section pointers for FDT and DomToIP

We introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm. Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
% in the coordinates corresponding to $x$.
If $C = g(I)$, it would be optimal. However we can only guarantee a factor of $g(I)^{|\spp(x)|}$. FDT iteratively solves linear programs that are about the same size as the description of $P(I)$.

@@

A subroutine of the FDT, called the DomToIP algorithm, finds feasible solutions to any IP with finite gap. This can be of independent interest, especially in proving that a model has unbounded gap.
\begin{restatable}{thm}{DomToIP}
	\label{domtoIP}
	Assume $1\leq g(I) < \infty$. The DomToIP algorithm finds $\hat{x}\in S(I)$ in polynomial time.
\end{restatable}

>>>>

In Section~\ref{binaryfdt} we introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm. Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
% in the coordinates corresponding to $x$.
If $C = g(I)$, it would be optimal. However we can only guarantee a factor of $g(I)^{|\spp(x)|}$. FDT iteratively solves linear programs that are about the same size as the description of $P(I)$.

@@

In Section~\ref{domTOIP} we describe a subroutine of the FDT, called the DomToIP algorithm, which finds feasible solutions to any IP with finite gap. This can be of independent interest, especially in proving that a model has unbounded gap.
\begin{restatable}{thm}{DomToIP}
	\label{domtoIP}
	Assume $1\leq g(I) < \infty$. The DomToIP algorithm finds $\hat{x}\in S(I)$ in polynomial time.
\end{restatable}
